Figures to insert in text

### 2018-03-12 Chapters/sdm-applications.tex
SDM Noise filter finished.

\chapter{Results (v): Supervised classification application}

@@

\chapter{Results (vi): Image noise filtering application}

@@

If the intersection between images becomes too high, the noise filter stops working. We have confirmed it writing letters ``B'', ``C'', ``D'' and numeral ``8''. They share a great amount of hard-locations and our noise filter stopped working. The training sets can be seen in Figure \ref{fig:filter-training2} and the results in Figure \ref{fig:filter-results2}.

@@

The chunck through exclusive OR (XOR) works because of the following theorem:

\begin{theorem}
If $v_1$ and $v_2$ are random bitstrings, then $\forall a, b, \mathbf{E} \left[ d(a \oplus v_1, b \oplus v_2) \right] = n/2$.
\end{theorem}
\begin{proof}
Let $\mathbb{A} = \{ i | a^i = b^i \}$ be the indexes in which the bits of $a$ are equal to the bits of $b$, and $\mathbb{B} = \{ i | a^i \ne b^i \}$ be indexes in which the bits of $a$ are different from the bits of $b$. Thus,

@@

In our example, we just used the right label to read each image. But, we could have used our classification algorithm already presented in this work as a pre-processing step, and then, with the correct label, run the noise filter.

\chapter{Results (vii): The possibility of unsupervised reinforcement learning}

>>>>

\chapter{Results (vi): Supervised classification application}

@@

\chapter{Results (vii): Image noise filtering application}

@@

If the intersection between images becomes too high, the noise filter stops working properly. We have confirmed it writing letters ``B'', ``C'', ``D'' and numeral ``8''. They share a great amount of hard-locations and our noise filter could not filter their noise correctly. The training sets can be seen in Figure \ref{fig:filter-training2} and the results in Figure \ref{fig:filter-results2}.

\begin{figure}[!htb]
  \subfloat[Letter ``B'' with 15\% of noise. ]{\includegraphics[width=0.5\textwidth]{./images02/filter/training2-b.png}}
  \subfloat[Letter ``C'' with 15\% of noise. ]{\includegraphics[width=0.5\textwidth]{./images02/filter/training2-c.png}}

  \subfloat[Letter ``D'' with 15\% of noise. ]{\includegraphics[width=0.5\textwidth]{./images02/filter/training2-d.png}}
  \subfloat[Letter ``8'' with 15\% of noise. ]{\includegraphics[width=0.5\textwidth]{./images02/filter/training2-8.png}}

  \caption{Training images in which the intersection between images is too high. They were written in their own addresses --- write(address=bs\_image, datum=bs\_image).}
  \label{fig:filter-training2}
\end{figure}

\begin{figure}[!htb]
  \captionsetup[subfigure]{labelformat=empty}
  \subfloat[]{\includegraphics[width=0.285\textwidth]{./images02/filter/case2-b-10noise.png}}

  \subfloat[]{\includegraphics[width=0.57\textwidth]{./images02/filter/case2-c-10noise.png}}

  \subfloat[]{\includegraphics[width=0.285\textwidth]{./images02/filter/case2-d-10noise.png}}

  \subfloat[]{\includegraphics[width=0.57\textwidth]{./images02/filter/case2-8-10noise.png}}

  \caption{When the intersection between images becomes too high, there appears some interference in the resulting image. All cases have 10\% noise. We can notice that the empty space in the right side of the ``C'' letter generates some white pixels in the right side of both ``B'' and ``D'' letters.
  \label{fig:filter-results2}
  }
\end{figure}

@@

\begin{figure}[!tb]
  \captionsetup[subfigure]{labelformat=empty}
  \subfloat[]{\includegraphics[width=\textwidth]{./images02/filter/labelB-20noise.png}}

  \subfloat[]{\includegraphics[width=\textwidth]{./images02/filter/labelC-20noise.png}}

  \subfloat[]{\includegraphics[width=\textwidth]{./images02/filter/labelD-20noise.png}}

  \subfloat[]{\includegraphics[width=\textwidth]{./images02/filter/label8-20noise.png}}

  \caption{Using labels solves the interference problem when the intersection between images becomes too high. All cases have 20\% noise.
  \label{fig:filter-results2-chunk}
  }
\end{figure}

The chunck through exclusive OR (XOR) works because of Theorem \ref{thm:xor-chuncks}, which says that chuncking the images with labels will generate, on average, orthogonal bitstrings. Thus, these orthogonal bitstrings will not interfere with each other because they share, on average, only one hardlocation.

The disadvantage of using labels is that it requires classification of the images. In our example, we just used the correct label with each image, but we could have used our classification algorithm as a pre-processing step, and only then run the noise filter.

\begin{theorem}
If $v_1$ and $v_2$ are random bitstrings, then $\forall a, b, \mathbf{E} \left[ d(a \oplus v_1, b \oplus v_2) \right] = n/2$.
\label{thm:xor-chuncks}
\end{theorem}
\begin{proof}
Let $\mathbb{A} = \{ i | a^i = b^i \}$ be the indexes in which the bits of $a$ are equal to the bits of $b$, and $\mathbb{B} = \{ i | a^i \ne b^i \}$ be indexes in which the bits of $a$ are different from the bits of $b$. Thus,

@@

\chapter{Results (viii): The possibility of unsupervised reinforcement learning}
